Theories of deliberated choice

### 2023-11-30 simple.tex
Much new stuff

\begin{abstract}
  TODO: abstract
\end{abstract}

@@

A claim $C$ is \emph{informative} iff $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
A claim $C$ is \emph{informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) ≠ P \cup \set{\emptyset}$.
A claim $C$ is \emph{strongly informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) \ssub P$.
% A claim $C$ is \emph{indicative} iff $\exists H \in \finite(\incr(\allhists)), i \in I \suchthat \pi(\set{{\allleadstog} \suchthat H \wsub \ileadstoinvg(P)} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
\begin{remark}
  Informativeness permits mere counting: the claim that exactly two persons deliberately believe $\phi$ is informative.
  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may want to know whether a given proposition is believed by a majority of individuals, or whether a given proposition is believed by nobody.
  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness.
  Note also that informativeness beyond counting implies informativeness.
  \Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.
\end{remark}

\begin{definition}[Anonymity]
  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in \allleadstos$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
  A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
\end{definition}
\begin{example}
  Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$. Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
\end{example}

\begin{theorem}
  For all exposure protocols, there exists a claim that holds and is strongly informative beyond counting and falsifiable iff $\exists i \suchthat P_i \neq \emptyset$.
\end{theorem}
\begin{proof}
  Define $C = \set{\allleadsto}$.
\end{proof}
\begin{theorem}
  For all exposure protocols, there exists a claim that holds and is informative beyond counting and falsifiable.
\end{theorem}
\begin{proof}
  Define $C = \set{\allleadsto}$.
\end{proof}
\begin{theorem}
  For all exposure protocols, there exists a claim that is anonymous, strongly informative beyond counting and falsifiable.
\end{theorem}
\begin{proof}
  Define the claim as $\forall i \in I, \hist \in \allhists: \hist \ileadstog \phi$.
\end{proof}

What about anonymous and holds?
\begin{theorem}
  For all exposure protocols, there exists a claim that holds and is anonymous.
\end{theorem}
\begin{proof}
  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
\end{proof}

\begin{theorem}
  Assume that $I = \set{i_1, i_2}$ and that $P_{i_1} = \phi$ and $P_{i_2} = ¬\phi$.

  Then, there exists a claim that holds and is anonymous and indicative.
\end{theorem}
\begin{proof}
  From $P_{i_1} = \phi$ we know that some $a_1$ is a decisive argument in favor of $\phi$ for $i_1$.
  From $P_{i_2} = ¬\phi$ we know that for some $\hist \in \allhists \suchthat a_1 \in \histend$, $\hist \nileadsto[i_2] \phi$ whereas $\hist \ileadsto[i_1] \phi$.
  Define $O = \set{(\hist, i_1)}$.
  Define 
  ${\allleadstog^1} = \set{(i_1, \ileadsto[i_1]), (i_2, \ileadsto[i_2])}$ and
  ${\allleadstog^2} = \set{(i_1, \ileadsto[i_2]), (i_2, \ileadsto[i_1])}$.
  Define the claim as $C = \set{{\allleadstog^1}, {\allleadstog^2}}$.
\end{proof}

\begin{theorem}
  Assume that $I = \set{i_1, i_2, i_3}$ and that $P_{i_1} = \phi$ and $P_{i_2} = P_{i_3} = ¬\phi$.

  Then, there exists a claim that holds and is anonymous and indicative.
\end{theorem}
\begin{proof}
  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
  In other words, for $k, l \in \intvl{1, 3}$, define
  ${\allleadstog^{k, l}} = \set{(i_k, \ileadsto[i_1]), (i_l, \ileadsto[i_2]), (i_{\intvl{1, 3} \setminus \set{k, l}}, \ileadsto[i_3])}$.
  Define the claim as $C = \set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}, {\allleadstog^{2, 1}}, {\allleadstog^{2, 3}}, {\allleadstog^{3, 1}}, {\allleadstog^{3, 2}}}$.

  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_2, a_3$ as arguments decisive in favor of $¬\phi$ for $i_2, i_3$.

  Define $\hist_{12} = (a_1, a_2)$ and $\hist_{13} = (\hist_{12}, a_1, a_3)$.
  We know that 
  $\hist_{12} \ileadsto[i_1] \phi$, 
  $\hist_{12} \ileadsto[i_2] ¬\phi$, 
  $\hist_{13} \ileadsto[i_1] \phi$, 
  $\hist_{13} \ileadsto[i_3] ¬\phi$.
  Define $\theta = \set{(\hist_{12}, i_1, \phi), (\hist_{13}, i_1, \phi)}$.
  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}}$, and $\pi(\set{{\allleadstog^{1, 2}}, {\allleadstog^{1, 3}}})(i_1) = \phi$.
\end{proof}

\begin{theorem}
  Assume that $I$ is finite and $P_{i_1} = \phi$ and $\forall i \in I \setminus \set{i_1}: P_i = ¬\phi$.

  Then, there exists a claim that holds and is anonymous and indicative.
\end{theorem}
\begin{proof}
  Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.

  Define $a_1$ as an argument decisive in favor of $\phi$ for $i_1$ and $a_i$ as arguments decisive in favor of $¬\phi$ for $i \in I \setminus \set{i_1}$.

  Assume (wlog) that $I = \set{i_1, …, i_{\card{I}}}$.
  Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{I}}$, $\hist_i = (\hist_{i - 1}, a_1, a_i)$.
  We know that, $\forall i \in \intvl{2, \card{I}}$: $\hist_i \ileadsto[i_1] \phi$ and $\hist_i \ileadsto[i] ¬\phi$.
  Define $\theta = \set{(\hist_i, i_1, \phi) \suchthat i \in \intvl{2, \card{I}}}$.

  Finally, the attitudes in $C$ compatible with $\theta$ are only $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C = \set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} = {\ileadsto[i_1]}})(i_1) = \phi$.
\end{proof}

$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
\begin{example}
  Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
  Then $\forall i: \ar \ileadstostg \phi$ is suitable.
  Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
\end{example}

@@

\subsection{Ideas for no suitable (new)}
$C$ must contain the real one.
Also, all the anonymously real ones.

\subsection{Ideas for no suitable}
Given $\histk \in \allhists$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
$\set{\histl \suchthat \histk \subset \histl \land \ar_l \in \histlend}$.
Given $\hist \in \allhists$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given $\ar_k, \ar_l \in \allargs$, let
$(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
$\cup_{\hist \in \allhists} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) =
  \set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend} =
  \set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given ${\ileadstog}$, $p \in P$, $s \in \allargs$ and $S \subseteq \allargs$, note that $s \in \ileadstoinvg(p)$ stand for $s \ileadstog p$ and $S \subseteq \ileadstoinvg(p)$ stand for $\forall s \in S: s \ileadstog p$.

@@

  This definition of truthfulness is adopted because of our goal of distinguishing empirical claims. Truthfulness, so defined, can be falsified empirically: if it does not hold, it is possible to prove this empirically by exhibiting a counter-example in the form of a tuple $i, k, (a_j)_{j \in \intvl{1, k}}, \alpha$ such that TODO.

@@

@@

TODO investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
Then exhibit a claim such that a smaller one is not the same status and a bigger one is not the same status.

>>>>

\begin{abstract}
  To be written.
\end{abstract}

@@

A claim $C$ is \emph{informative} iff $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
A claim $C$ is \emph{informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) ≠ P \cup \set{\emptyset}$.
A claim $C$ is \emph{strongly informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) \ssub P$.
% A claim $C$ is \emph{indicative} iff $\exists H \in \finite(\incr(\allhists)), i \in I \suchthat \pi(\set{{\allleadstog} \suchthat H \wsub \ileadstoinvg(P)} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
\begin{remark}
  Informativeness permits mere counting: the claim that exactly two persons deliberately believe $\phi$ is informative.
  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may want to know whether a given proposition is believed by a majority of individuals, or whether a given proposition is believed by nobody.
  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness.
  Note also that informativeness beyond counting implies informativeness.
\end{remark}
\begin{remark}
  We could weaken indicativeness by allowing for disjuncts: observing either that $\hist \ileadsto \phi$ or that $\hist \ileadsto \psi$ permits to deduce something about $P_i$.
  (Or more complex formulas under the form of a set of possible functions in $P^H$?)
  (Actually I am not sure that this really weakens the condition.)
\end{remark}

\begin{definition}[Anonymity]
  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in \allleadstos$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
  A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
\end{definition}
\Cref{ex:anon} illustrates.

We are now interested in the interplay between properties of holding, anonymity, (strong) informativeness beyond counting, and falsifiability.
\Cref{th:hsif,th:hif,th:asif} show their compatibility when one of holding or anonymity is not required (except that informativeness beyond counting cannot be made strong in the edge case where $\forall i \in I: P_i = \emptyset$).

We thus turn to requiring both anonymous and holding.
They are always satisfiable when only these two are required (\cref{th:ha}).
\Cref{th:infoBeyonCKO} (and extensions, \cref{th:infoBeyonCKOext,th:strinfoBeyonCKO}) shows that informativeness beyond counting (and variants) is too demanding if one wants to investigate situations where individuals have differing deliberate preferences.

It is possible under reasonable conditions of regularity to satisfy anonymous and holding together with indicativeness. This happens for example when everybody has a deliberate judgment and a finite set of decisive arguments suffices to lead everybody to their deliberate judgment (\cref{th:suffIndicDec}).

\begin{theorem}
  \label{th:suffFals}
  Assume that $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
  Then, there exists a claim that holds and is anonymous and falsifiable.
\end{theorem}
\begin{proof}
  Define $C = \set{{\allleadstog} \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$. It holds and is anonymous.
  Pick any ${\allleadstog} \notin C$.
  Then, $\exists i \in I \suchthat {{\ileadstog}} \notin \set{{\ileadsto[k]} \suchthat k \in I}$.
  Pick any such $i$ and any $H$ such that $\forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
  Define $\theta = \set{(\hist, i, {\ileadstog}(\hist)) \suchthat \hist \in H} \in \Theta \cap \powerset{\allleadstog}$.
  Then, $\theta \notin C^\wsub$, because $\forall j \in I: \theta \nsubseteq {\ileadsto[j]}$.

  For another proof, note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat \forall i \in I: \exists j \in I \suchthat \theta \cap (\allhists × \set{i} × P) \wsub {\ileadsto[j]}}$.
  Pick any ${\allleadstog} \in E(C^\wsub \cap \Theta)$ and let us show that ${\allleadstog} \in C$.
  Note that ${\allleadstog} \notin C \iff \exists i \in I \suchthat {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, in which case the consequent in the theorem holds.
  We need to show that $\nexists i \in I, H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
  In other words, given any $i \in I$, we need to show that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.
\end{proof}

\begin{remark}
  The opposite of \cref{th:suffFals} is NOT $\forall {\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}: \exists H \in \finite(\incr(\allhists)) \suchthat \forall j \in I: \exists \hist \in H \suchthat {\ileadstog}(\hist) \neq {\ileadsto[j]}(\hist)$.
  Thus, for some ${\allleadstog} \in \allleadstos$ and some $i \in I$ with ${\ileadstog} \in P^{\allhists} \setminus \set{{\ileadsto[k]} \suchthat k \in I}$, we have that $\forall H \in \finite(\incr(\allhists)): \exists j \in I \suchthat \forall \hist \in H: {\ileadstog}(\hist) = {\ileadsto[j]}(\hist)$.

  For example, $\allargs = \set{\ar_1, \ar_2}$ and ${\ileadstog}$ is $\phi$ when the path starts with $\ar_1$ (or is empty) and is $¬\phi$ when the path starts with $\ar_2$ and the attitude contains only people constant to $\phi$ (except that they map $\emptyset$ to anything) and people constant to $¬\phi$ (except that they map $\emptyset$ to anything).
\end{remark}
\begin{theorem}
  Consider the attitude above. Is there a claim that holds and is anonymous and falsifiable?
  Check \cref{ex:falsAnonIfBig}.
\end{theorem}

\subsection{Ideas for no suitable}
$C$ is \emph{suitable} iff it holds and is anonymous, informative and falsifiable.
\begin{example}
  Assume that $\exists \ar, \phi \suchthat \forall i: \ar \ileadstost \phi$.
  Then $\forall i: \ar \ileadstostg \phi$ is suitable.
  Note that it is falsifiable but not verifiable (that is, no $O$ implies $C$).
\end{example}

@@

Given $\histk \in \allhists$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
$\set{\histl \suchthat \histk \subset \histl \land \ar_l \in \histlend}$.
Given $\hist \in \allhists$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given $\ar_k, \ar_l \in \allargs$, let
$(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
$\cup_{\hist \in \allhists} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) =
  \set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend} =
  \set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given ${\ileadstog}$, $p \in P$, $s \in \allargs$ and $S \subseteq \allargs$, note that $s \in \ileadstoinvg(p)$ stand for $s \ileadstog p$ and $S \subseteq \ileadstoinvg(p)$ stand for $\forall s \in S: s \ileadstog p$.

@@

  This definition of truthfulness is adopted because of our goal of distinguishing empirical claims. Truthfulness, so defined, can be falsified empirically: if it does not hold, it is possible to prove this empirically by exhibiting a counter-example in the form of a tuple $i, k, (a_j)_{j \in \intvl{1, k}}, \alpha$ such that … (to be completed).

@@

  \begin{example}
    \label{ex:anon}
    Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$. Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
  \end{example}

  \begin{example}
    Consider $I = \set{i}$ and $\ar_1 \neq \ar_2 \in \allargs$.
    The claim $C = \set{{\allleadstog} \in \allleadstos \suchthat (\forall \hist \neq \emptyset: \hist \ileadstog \phi) \lor (\forall \hist \neq \emptyset: \hist \ileadstog ¬\phi)}$ is not falsifiable.

    Consider ${\allleadstog}$ defined as $\hist \ileadstog \phi$ iff $\hist = \emptyset \lor \hist_1 = \ar_1$ and $\hist \ileadstog ¬\phi$ otherwise.
    We have ${\allleadstog} \notin C$.
    But any $θ \subseteq {\allleadstog}$ satisfies $\theta \in C^\wsub$.
  \end{example}

  \begin{example}
    \label{ex:falsAnonIfBig}
    Consider $I = \set{i_1, i_2}$ and $\ar_1 \neq \ar_2 \in \allargs$.
    Given $p_0, p, p'_0, p' \in P$,
    define ${\allleadstog^{i_1 \mapsto (p_0, p); i_2 \mapsto (p'_0, p')}}$ as $\emptyset \ileadstog[i_1] p_0 \land \emptyset \ileadstog[i_2] p'_0 \land \forall \hist \in \allhists \setminus \set{\emptyset}: \hist \ileadstog[i_1] p \land \hist \ileadstog[i_2] p'$.

    The claim $C = \set{{\allleadstog^{i_1 \mapsto (p_0, p); i_2 \mapsto (p'_0, p')}} \suchthat p_0, p, p'_0, p' \in \set{\phi, ¬\phi}}$ is not falsifiable.
    Consider ${\allleadstog}$ defined as, $\forall i \in I$, $\hist \ileadstog \phi$ iff $\hist = \emptyset \lor \hist_1 = \ar_1$ and $\hist \ileadstog ¬\phi$ otherwise.
    We have ${\allleadstog} \notin C$.

    Consider now any bigger claim $C'$, thus with $C \wsub C'$.
    I believe that $C'$ is falsifiable iff it includes all relations that are constant on all paths starting with a given argument (thus all $\allleadstog$ such that $\forall \hist, \histp \in \allhists: \hist_1 = \histp_1 \implies {\ileadstog}(\hist) = {\ileadstog}(\histp)$).
  \end{example}

  \begin{example}
    Consider $I = \set{i_{p_0, p} \suchthat p_0, p \in \set{\phi, ¬\phi}}$ (thus $\card{I} = 4$).
    Given $p_0, p \in P$,
    define $R^{(p_0, p)} = R^{\emptyset \mapsto p_0; p}: \allhists \rightarrow P$ as $R(\emptyset) = p_0 \land \forall \hist \in \allhists \setminus \set{\emptyset}: R(\hist) = p$.

    Define ${\allleadsto}$ as $\forall p_0, p \in \set{\phi, ¬\phi}: {\ileadsto[i_{p_0, p}]} = R^{\emptyset \mapsto p_0; p}$.

    Given $f: I \rightarrow \set{\phi, ¬\phi}^2$,
    define ${\allleadstog^f}$ as $\forall i \in I: {\allleadstog^f_i} = R^{f(i)}$.
    Note that any $f \in (\set{\phi, ¬\phi}^2)^I$ can be seen as a permutation $\sigma$ over $I$ and that ${\allleadstog^f} = {\allleadsto} \circ \sigma$.

    The claim $C = \set{{\allleadstog^f} \suchthat f \in (\set{\phi, ¬\phi}^2)^I}$ is falsifiable: consider any ${\allleadstog}$ observably compatible with $C$; if there is $\hist^1, \hist^2, \hist^3 \in \allhists \setminus \set{\emptyset}$ and $i_1 \neq i_2 \neq i_3 \neq i_1 \in I$ with $\forall k \in \intvl{1, 3}: \hist^k \ileadstog[i_k] \phi$, then ${\allleadstog}$ is not observably compatible with $C$, so there must be at most 2 individuals mapping some non empty path to $\phi$ (thus at least 2 mapping all non empty paths to $¬\phi$) and for the same reason, at least 2 individuals mapping all non empty paths to $\phi$; thus (together with noting that two individuals mapping every paths to $\phi$ is not observably compatible with $C$ and adding the missing bits), ${\allleadstog} \in C$.
  \end{example}

  \begin{example}
    Consider $I = \cup_{p_0, p \in \set{\phi, ¬\phi}} I_{p_0, p}$, with each $I_{p_0, p}$ infinite, and $\ar_1 \neq \ar_2 \in \allargs$.
    Given $p_0, p \in P$,
    define $R^{(p_0, p)} = R^{\emptyset \mapsto p_0; p}: \allhists \rightarrow P$ as $R(\emptyset) = p_0 \land \forall \hist \in \allhists \setminus \set{\emptyset}: R(\hist) = p$.
    Define ${\allleadsto}$ as $\forall p_0, p \in \set{\phi, ¬\phi}, i \in I_{p_0, p}: {\ileadsto} = R^{\emptyset \mapsto p_0; p}$.

    The claim $C = \set{{\allleadsto} \circ \sigma \suchthat \sigma: I \leftrightarrow I}$ is not falsifiable:
    consider ${\allleadstog}$ defined as, $\forall i \in I$, $\hist \ileadstog \phi$ iff $\hist = \emptyset \lor \hist_1 = \ar_1$ and $\hist \ileadstog ¬\phi$ otherwise; we have ${\allleadstog} \notin C$
    but any $θ \in \Theta, \theta \subseteq {\allleadstog}$ satisfies $\theta \in C^\wsub$.

    Now consider $C' = \set{{\allleadstog} \suchthat \forall i \in I, \hist, \histp \in \allhists: \hist_1 = \histp_1 \implies {\ileadstog}(\hist) = {\ileadstog}(\histp)}$. (Thus $C \wsub C'$.)
    This one is falsifiable: if ${\allleadstog} \notin C$, then $\exists i \in I, \hist, \histp \suchthat \hist_1 = \histp_1 \land {\ileadstog}(\hist) ≠ {\ileadstog}(\histp)$, now define $\histpp$ as the common prefix to $\hist$ and $\histp$; as ${\ileadstog}(\hist) ≠ {\ileadstog}(\histp)$, we have at least one of ${\ileadstog}(\hist) ≠ {\ileadstog}(\histpp)$ or ${\ileadstog}(\histp) ≠ {\ileadstog}(\histpp)$, and as $\histpp$ satisfies $\histpp_1 = \hist_1$ and $\histpp_1 = \histp_1$, observing the corresponding pair of paths for $i$ falsifies $C$.
  \end{example}

  \begin{example}
    Imagine that the real relation is composed of individuals who map $(a_1, a_2)$ to $\phi$ and $(a_1, a_3)$ to $¬\phi$ and individuals converse (with both, say, mapping everything else to $0$).
    Then the claim $C = \set{{\allleadstog} \suchthat \forall i \in I: {\ileadstog}(\ar_1, \ar_2) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_1, \ar_3) \in \set{\phi, ¬\phi}}$ is falsifiable.

    Imagine that the real relation is composed of individuals who map $(a_1, a_2)$ to $\phi$ and $(a_1, a_3)$ to $¬\phi$ and individuals converse (with both, say, mapping everything else to $0$) and individuals who map $(a_4, a_5)$ to $\phi$ and $(a_6)$ to $¬\phi$ and individuals converse, with both mapping everything else to $0$.
    Then the claim $C = \set{{\allleadstog} \suchthat \forall i \in I: [{\ileadstog}(\ar_1, \ar_2) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_1, \ar_3) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0] \lor [{\ileadstog}(\ar_4, \ar_5) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_6) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0]}$, where $H$ designates all “other” paths (abusing notation), is falsifiable.

    Imagine that the real relation is composed of individuals who map $(a_1, a_2)$ to $\phi$ and $(a_1, a_3)$ to $¬\phi$ and individuals converse (with both, say, mapping everything else to $0$) and individuals who map $(a_1, a_4)$ to $\phi$ and $(a_6)$ to $¬\phi$ and individuals converse, with both mapping everything else to $0$.
    Then the claim $C = \set{{\allleadstog} \suchthat \forall i \in I: [{\ileadstog}(\ar_1, \ar_2) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_1, \ar_3) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0] \lor [{\ileadstog}(\ar_1, \ar_4) \in \set{\phi, ¬\phi} \land {\ileadstog}(\ar_6) \in \set{\phi, ¬\phi} \land {\ileadstog}(H) = 0]}$, where $H$ designates all “other” paths (abusing notation), is falsifiable: could have an individual mapping both $(\ar_1, \ar_2)$ and $(\ar_1, \ar_4)$ to $0$ but then if she maps $\ar_6$ to $0$, observe both $(\ar_1, \ar_2)$ and $\ar_6$ and falsify $C$; if she maps $\ar_6$ in $\set{\phi, ¬\phi}$, both $(\ar_1, \ar_4)$ and $\ar_6$ and falsify $C$ (here assuming falsely in the whole example that $\ar_6$ can be observed together with $(\ar_1, .)$, so we probably should replace $\ar_6$ by $\emptyset$).
  \end{example}

  \subsection{Compatibility of claim properties}
  \begin{theorem}
    \label{th:hsif}
    For all exposure protocols, there exists a claim that holds and is strongly informative beyond counting and falsifiable iff $\exists i \suchthat P_i \neq \emptyset$.
  \end{theorem}
  \begin{proof}
    Define $C = \set{\allleadsto}$.
  \end{proof}
  \begin{theorem}
    \label{th:hif}
    For all exposure protocols, there exists a claim that holds and is informative beyond counting and falsifiable.
  \end{theorem}
  \begin{proof}
    Define $C = \set{\allleadsto}$.
  \end{proof}
  \begin{theorem}
    \label{th:asif}
    For all exposure protocols, there exists a claim that is anonymous, strongly informative beyond counting and falsifiable.
  \end{theorem}
  \begin{proof}
    Define the claim as $\forall i \in I, \hist \in \allhists: \hist \ileadstog \phi$.
  \end{proof}

  \begin{theorem}
    \label{th:ha}
    For all exposure protocols, there exists a claim that holds and is anonymous.
  \end{theorem}
  \begin{proof}
    Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
  \end{proof}

  \begin{theorem}
    \label{th:suffIndic}
    Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
    Then, there exists a claim that holds and is anonymous and indicative.
  \end{theorem}
  \begin{proof}
    Define $p = P_{i_1}$.
    Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
    The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
  \end{proof}
  \begin{corollary}
    \label{th:suffIndicDec}
    Assume that for some $p \in P$, we have $\exists i \in I \suchthat P_i = p$ and $\forall i_2 \suchthat P_{i_2} \neq p$ we have that $\exists A \in \finite(\allargs) \suchthat \forall i \in I \suchthat P_i \neq p, \exists a \in A \suchthat {\ileadstost}(a) \in P \setminus \set{p}$, then there exists a claim that holds and is anonymous and indicative.
  \end{corollary}
  \begin{proof}
    We know that $i_1$ has some decisive argument $a_1$ in favor of $p$.
    Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
    Apply \cref{th:suffIndic}.
  \end{proof}

@@

Consider: investigate claims that are non falsifiable but with $C^\wsub \cap \Theta \neq \Theta$.
Then exhibit a claim such that a smaller one is not the same status and a bigger one is not the same status.
